### 2016-07-10 Projects/DelCo_2012/Report/DelCo_2012.tex
Added Abstract, keywords and start of Summary

@@

movement, sweeping nozzle, etc -- more efficient cooling / more effective that the type of nozzle or the amount of suppressive agent.

@@

>>>>

Experiments were conducted to investigate the capabilities and limitations of compressed air foam (CAF) relative to water when used for interior structural firefighting.  The key outcomes were to measure the gas cooling and fire suppression capabilities of CAF compared to water. The experimental designs were developed based on a project planning workshop led by the Fire Protection Research Foundation.  Incidents where firefighters had experienced burn injuries or other challenges while using CAF during interior attack operations in residential occupancies served as the catalyst for this study.

Full scale fire experiments designed to address those questions were conducted over a period of years from 2012 through 2015. The experimental arrangements and results are presented in this report.  The results from both the gas cooling and the suppression of residential scale room fires showed the effectiveness of water and CAF hose streams to be similar.  Under the test conditions both agents were effective.  This study did not address the previously documented attributes of CAF for improved exposure protection and improved prevention of a fire re-kindle, relative to plain water.

This study conducted by NIST, was part of a larger research project led by California Polytechnic State University (Cal Poly), San Luis Obispo in collaboration with the Montgomery County (MD) Fire and Rescue Service.  This study was supported in part by a DHS/FEMA Assistance to Firefighters Research and Development Grant.

\vspace{0.5in}
Key words: compressed air foam, fire experiments, firefighting, fire suppression, fuel load, gas cooling, structural firefighting, suppression research

@@

movement, sweeping nozzle, etc -- more efficient cooling / more effective that the type of nozzle or the amount of suppressive agent.
air entrainment - ref hose stream study.

@@

Experiments were conducted to investigate the capabilities and limitations of compressed air foam (CAF) relative to water when used for interior structural firefighting.  The experimental designs were developed based on a project planning workshop led by the Fire Protection Research Foundation.  The key outcomes were to measure the gas cooling and fire suppression capabilities of CAF compared to water. Incidents where firefighters had experienced burn injuries or other challenges while using CAF during interior attack operations in residential occupancies served as the catalyst for this study.

Full scale fire experiments designed to address those questions were conducted over a period of years from 2012 through 2015. The experimental arrangements were designed to be representative of residential fire scenarios.

Gas Cooling

Fire Suppression

The results from both the gas cooling and the suppression of residential scale room fires showed the effectiveness of water and CAF hose streams to be similar.  Under the test conditions both agents were effective.  This study did not address the previously documented attributes of CAF for improved exposure protection and improved prevention of a fire re-kindle, relative to plain water.

This study conducted by NIST, was part of a larger research project led by California Polytechnic State University (Cal Poly), San Luis Obispo in collaboration with the Montgomery County (MD) Fire and Rescue Service.  This study was supported in part by a DHS/FEMA Assistance to Firefighters Research and Development Grant.
